---
title: "Clean CareCoord_patients data"
author: "Esther Lips"
date: "8-11-2017"
output: html_document
---
This markdown file describes the cleaning of the Care coordinates Patients file.

STEP 0: load packages
```{r Load packages}
library("tidyr")
library("dplyr")
rm(list=ls())
```

STEP 1: Read in data

```{r Read data}
ds1 <- tbl_df(read.csv("data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-1-5750335-11-13-2017-1510643630161.csv", skip = 2, colClasses = "character"))
ds2 <- tbl_df(read.csv("data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-2-5750335-11-13-2017-1510643645266.csv", skip = 2, colClasses = "character"))
ds3 <- tbl_df(read.csv("data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-3-5750335-11-13-2017-1510643659062.csv", skip = 2, colClasses = "character"))
ds4 <- tbl_df(read.csv("data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-4-5750335-11-13-2017-1510643672475.csv", skip = 2, colClasses = "character"))
ds5 <- tbl_df(read.csv("data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-5-5750335-11-13-2017-1510643684478.csv", skip = 2, colClasses = "character"))

head <- read.table('data/RawData-CareCoordinationPatients-11-13-2017/RawData-Part-1-5750335-11-13-2017-1510643630161.csv', nrows = 2, header = FALSE, sep =',', stringsAsFactors = FALSE)

# Load LUT file
LUT <- tbl_df(read.csv2("./data/LUT_v2.csv", sep=',', header=T, colClasses = "character"))

# Remove first line, because it contains subquestion headers
ds1 <- ds1[-1,]
ds2 <- ds2[-1,]
ds3 <- ds3[-1,]
ds4 <- ds4[-1,]
ds5 <- ds5[-1,]

# Concat all data
ccp_raw <- rbind(ds1, ds2, ds3, ds4, ds5)
#dim(ccp_raw)

# include only responses with Seq..Number 1
ccp_raw <- ccp_raw[which(ccp_raw$Seq..Number ==1),]

print(paste("This CCP data has", nrow(ccp_raw), "responses."))

# Add 'verwerkings code' column to moc file and initialize it with 'NM', which stands for 'non matching'.
ccp_raw$verw_code <- "NM"

```


Correct ClinicNames in raw data with the ones in Lookup table (LUT)

```{r Match on ClinicNames}
c_name.idx <- match(tolower(ccp_raw$clinic), tolower(LUT$c_name), nomatch=0)
c_name2.idx <- match(tolower(ccp_raw$clinic), tolower(LUT$c_name2), nomatch=0) 
c_name3.idx <- match(tolower(ccp_raw$clinic), tolower(LUT$c_name3), nomatch=0)

notnull_nm1 <- which(c_name.idx !=0)
notnull_nm2 <- which(c_name2.idx > 1) # skip also 1, which matches to ''
notnull_nm3 <- which(c_name3.idx > 1) # skip also 1, which matches to ''

#length(notnull_nm1)
#[1] 13881
#length(notnull_nm2)
# [1] 93
#length(notnull_nm3)
#[1] 173

ccp_raw$country[notnull_nm1] <- LUT$country[c_name.idx]
ccp_raw$clinic[notnull_nm1] <- LUT$c_name[c_name.idx]
ccp_raw$clinic_id[notnull_nm1] <- LUT$c_id[c_name.idx]
ccp_raw$verw_code[notnull_nm1] <- "VCNM"

ccp_raw$country[notnull_nm2] <- LUT$country[c_name2.idx[notnull_nm2]]
ccp_raw$clinic[notnull_nm2] <- LUT$c_name[c_name2.idx[notnull_nm2]]
ccp_raw$clinic_id[notnull_nm2] <- LUT$c_id[c_name2.idx[notnull_nm2]]
ccp_raw$verw_code[notnull_nm2] <- "VCNM"

ccp_raw$country[notnull_nm3] <- LUT$country[c_name3.idx[notnull_nm3]]
ccp_raw$clinic[notnull_nm3] <- LUT$c_name[c_name3.idx[notnull_nm3]]
ccp_raw$clinic_id[notnull_nm3] <- LUT$c_id[c_name3.idx[notnull_nm3]]
ccp_raw$verw_code[notnull_nm3] <- "VCNM"

nr_names = length(notnull_nm1)+length(notnull_nm2)+length(notnull_nm3)

print(paste("In total",nr_names,"matches on ClinicNames are found."))
```

Check whether the instances that could not be matched on clinic names can be matched on clinic_id
```{r match on ClinicID}
#length(which(ccp_raw$verw_code == 'NM'))
#[1] 6776
nm.idx <- which(ccp_raw$verw_code == 'NM')
nm_ccp_raw <- ccp_raw[nm.idx,]
nm_ccp_raw$index <- nm.idx

# match clinic_id name on subset
cid1.idx <- match(nm_ccp_raw$clinic_id, LUT$c_id, nomatch=0)
notnull_c1 <- which(cid1.idx !=0)
#length(notnull_c1)
# [1]  3338

cid2.idx <- match(nm_ccp_raw$clinic_id, LUT$c_id2, nomatch=0)
notnull_c2 <- which(cid2.idx > 1)
#length(notnull_c2)
#[1] 67

cid3.idx <- match(nm_ccp_raw$clinic_id, LUT$c_id3, nomatch=0)
notnull_c3 <- which(cid3.idx > 1)
#length(notnull_c3)
#[1] 5

nm_ccp_raw$country[notnull_c1] <- LUT$country[cid1.idx]
nm_ccp_raw$clinic[notnull_c1] <- LUT$c_name[cid1.idx]
nm_ccp_raw$clinic_id[notnull_c1] <- LUT$c_id[cid1.idx]
nm_ccp_raw$verw_code[notnull_c1] <- "VCID"

nm_ccp_raw$country[notnull_c2] <- LUT$country[cid2.idx[notnull_c2]]
nm_ccp_raw$clinic[notnull_c2] <- LUT$c_name[cid2.idx[notnull_c2]]
nm_ccp_raw$clinic_id[notnull_c2] <- LUT$c_id[cid2.idx[notnull_c2]]
nm_ccp_raw$verw_code[notnull_c2] <- "VCID"

nm_ccp_raw$country[notnull_c3] <- LUT$country[cid3.idx[notnull_c3]]
nm_ccp_raw$clinic[notnull_c3] <- LUT$c_name[cid3.idx[notnull_c3]]
nm_ccp_raw$clinic_id[notnull_c3] <- LUT$c_id[cid3.idx[notnull_c3]]
nm_ccp_raw$verw_code[notnull_c3] <- "VCID"

sb.idx <- which(nm_ccp_raw$verw_code != 'NM')
ccp_raw[nm_ccp_raw$index[sb.idx], 8:10] <- nm_ccp_raw[sb.idx, 8:10]
ccp_raw[nm_ccp_raw$index[sb.idx], 95] <- nm_ccp_raw[sb.idx, 95]

nr_names = length(notnull_c1)+length(notnull_c3)+length(notnull_c3)

print(paste("In total",nr_names,"matches on ClinicIDs are found."))
```
Correct country names and check matches

```{r correct CountryNames}
#length(which(ccp_raw$verw_code == 'NM'))
# 3365
#length(which(ccp_raw$verw_code == 'VCID'))
#[1] 3410
#length(which(ccp_raw$verw_code == 'VCIP'))
#[1] 0
#length(which(ccp_raw$verw_code == 'VCNM'))
# [1] 14102

# substitute all variances on saudi arabia to 'Saudi Arabia'
ccp_raw$country <- sub("^saudi(.*)",'Saudi Arabia', ccp_raw$country, ignore.case = TRUE)

# substitute all variances on New Zealand to 'New Zealand'
ccp_raw$country <- sub("^New(.*)",'New Zealand', ccp_raw$country, ignore.case = TRUE)

# substitute all variances on portugal to 'Portugal'
ccp_raw$country <- sub("^portugal(.*)",'Portugal', ccp_raw$country, ignore.case = TRUE)

# substitute all variances on Italy to 'Italy'
ccp_raw$country <- sub("^italy(.*)",'Italy', ccp_raw$country, ignore.case = TRUE)

# substitute all variances on Kazakstan to 'Kazakhstan'
ccp_raw$country <- sub("^kazas(.*)",'Kazakhstan', ccp_raw$country, ignore.case = TRUE)

ccp_raw$verw_code <- as.factor(ccp_raw$verw_code)
ccp_raw$country <- as.factor(ccp_raw$country)
table(ccp_raw$country, ccp_raw$verw_code)
```

14-11 Update ClinicNames with short names

```{r Update Clinic Names}
update_names <- tbl_df(read.csv2("./data/LUT_v3.csv", sep=',', header=T, colClasses = "character"))

c.idx <- match(ccp_raw$clinic_id, update_names$c_id, nomatch=0)
notnull <- which(c.idx != 0)

df <- data.frame(matrix(ncol = 4, nrow = length(notnull)))
df[,1] <- ccp_raw$clinic_id[notnull]
df[,2] <- ccp_raw$clinic[notnull]
df[,3] <- update_names$c_id[c.idx]
df[,4] <- update_names$c_name[c.idx]

ccp_raw$clinic[notnull] <- update_names$c_name[c.idx]

# check whether procedure went ok
#ccp_raw$clinic[which(ccp_raw$clinic_id == 1502)]
```

Recode column 41 
```{r recode Columns}
recode_cols <- c(41)

# backup data
ccp_copy <- ccp_raw

for(c in 1:length(recode_cols)) 
{
  col <- recode_cols[c]
  #print(col)
  r1.idx <- which(ccp_raw[,col] == 5)
  r2.idx <- which(ccp_raw[,col] == 4)
  r3.idx <- which(ccp_raw[,col] == 3)
  r4.idx <- which(ccp_raw[,col] == 2)
  r5.idx <- which(ccp_raw[,col] == 1)
  
  ccp_raw[r1.idx,col] <- 1
  ccp_raw[r2.idx,col] <- 2
  ccp_raw[r3.idx,col] <- 3
  ccp_raw[r4.idx,col] <- 4
  ccp_raw[r5.idx,col] <- 5
}
```

Save files with and without verwerkingscode
```{r Save files}
# make header
header <- mat.or.vec(nrow(head), ncol(ccp_raw))
header <- cbind(head, header)
header <- rbind(header, names(ccp_raw))
header[1,which(header[1,] == 0)] <- ''
header[2,which(header[2,] == 0)] <- ''

# add empty line below header
empty_line <- c(rep('',ncol(header)))
header <- rbind(header, empty_line)

ccp_raw <- ccp_raw[which(ccp_raw$verw_code != 'NM'),]
#dim(ccp_raw)
# [1] 17512    95

write.table(header[,1:94], file = "data/FINAL/CCP/Clean-5750335-11-14-2017.csv", row.names=F, col.names=F,fileEncoding = "UTF-8",sep=',')
write.table(ccp_raw[,1:94], file = "data/FINAL/CCP/Clean-5750335-11-14-2017.csv", row.names=F, col.names=F,fileEncoding = "UTF-8", append=T, sep=',')

write.table(header[,1:ncol(ccp_raw)], file = "data/FINAL/CCP/Clean-5750335-11-14-2017-verwerkingcode.csv", row.names=F, col.names=F,fileEncoding = "UTF-8",sep=',')
write.table(ccp_raw, file = "data/FINAL/CCP/Clean-5750335-11-14-2017-verwerkingcode.csv", row.names=F, col.names=F,fileEncoding = "UTF-8", append=T, sep=',')

```
