---
title: "Clean CareCoord_patients data"
author: "Esther Lips"
date: "3-11-2017"
output: html_document
---
This markdown file describes the cleaning of the Care coordinates Patients file.

STEP 0: load packages
```{r Load packages}
library("tidyr")
library("dplyr")
rm(list=ls())
```

STEP 1: Read in data

```{r Read data}
ps1 <- tbl_df(read.csv("data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-1-5783064-11-13-2017-1510643044891.csv", skip = 2, colClasses = "character"))
ps2 <- tbl_df(read.csv("data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-2-5783064-11-13-2017-1510643091066.csv", skip = 2, colClasses = "character"))
ps3 <- tbl_df(read.csv("data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-3-5783064-11-13-2017-1510643136856.csv", skip = 2, colClasses = "character"))
ps4 <- tbl_df(read.csv("data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-4-5783064-11-13-2017-1510643181827.csv", skip = 2, colClasses = "character"))
ps5 <- tbl_df(read.csv("data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-5-5783064-11-13-2017-1510643224551.csv", skip = 2, colClasses = "character"))

# read lut file
LUT <- tbl_df(read.csv2("./data/LUT_v2.csv", sep=',', header=T, colClasses = "character"))

# initialize header
head <- read.table('data/RawData-PatientSatisfaction-11-13-2017/RawData-Part-1-5783064-11-13-2017-1510643044891.csv', nrows = 2, header = FALSE, sep =',', stringsAsFactors = FALSE)

# concat data
ps_raw <- rbind(ps1, ps2, ps3, ps4, ps5)

# remove id with seq...number not 1
ps_raw <- ps_raw[which(ps_raw$Seq..Number == 1),]

# add columns to data file
ps_raw$rowMeans <- ""
ps_raw$patient_type <- ""
ps_raw$verw_code <- "NM"

print(paste("In total this file has", nrow(ps_raw)," responses."))
```

```{r define PatientTypes}
ps_raw$patient_type[which(ps_raw[,36] != '')] <- 'HD'
ps_raw$patient_type[which(ps_raw[,43] != '')] <- 'Home HD/PD'
ps_raw$patient_type[which(ps_raw[,50] != '')] <- "Clinic Consult"
```

Match column ps_raw with the different clinic_names in LUT

```{r Match Clinic Names}
c_name.idx <- match(tolower(ps_raw$clinic), tolower(LUT$c_name), nomatch=0)
c_name2.idx <- match(tolower(ps_raw$clinic), tolower(LUT$c_name2), nomatch=0) 
c_name3.idx <- match(tolower(ps_raw$clinic), tolower(LUT$c_name3), nomatch=0)

notnull_nm1 <- which(c_name.idx !=0)
notnull_nm2 <- which(c_name2.idx > 1) # skip also 1, which matches to ''
notnull_nm3 <- which(c_name3.idx > 1) # skip also 1, which matches to ''

nr_names = length(notnull_nm1)+length(notnull_nm2)+length(notnull_nm3)

print(paste("In total",nr_names,"matches on ClinicNames are found."))
```
```{r Correct ClinicNames}
ps_raw$country[notnull_nm1] <- LUT$country[c_name.idx]
ps_raw$clinic[notnull_nm1] <- LUT$c_name[c_name.idx]
ps_raw$clinic_id[notnull_nm1] <- LUT$c_id[c_name.idx]
ps_raw$verw_code[notnull_nm1] <- "VCNM"

ps_raw$country[notnull_nm2] <- LUT$country[c_name2.idx[notnull_nm2]]
ps_raw$clinic[notnull_nm2] <- LUT$c_name[c_name2.idx[notnull_nm2]]
ps_raw$clinic_id[notnull_nm2] <- LUT$c_id[c_name2.idx[notnull_nm2]]
ps_raw$verw_code[notnull_nm2] <- "VCNM"

ps_raw$country[notnull_nm3] <- LUT$country[c_name3.idx[notnull_nm3]]
ps_raw$clinic[notnull_nm3] <- LUT$c_name[c_name3.idx[notnull_nm3]]
ps_raw$clinic_id[notnull_nm3] <- LUT$c_id[c_name3.idx[notnull_nm3]]
ps_raw$verw_code[notnull_nm3] <- "VCNM"
```

Check whether the instances that could not be matched on clinic names can be matched on clinic_id

```{r Match Clinic Names}
#length(which(ps_raw$verw_code == 'NM'))
#[1] 6312
nm.idx <- which(ps_raw$verw_code == 'NM')
nm_ps_raw <- ps_raw[nm.idx,]
nm_ps_raw$index <- nm.idx

# match clinic_id name on subset
cid1.idx <- match(nm_ps_raw$clinic_id, LUT$c_id, nomatch=0)
notnull_c1 <- which(cid1.idx !=0)
#length(notnull_c1)
# [1] 3943

cid2.idx <- match(nm_ps_raw$clinic_id, LUT$c_id2, nomatch=0)
notnull_c2 <- which(cid2.idx > 1)
#length(notnull_c2)
#[1] 90

nr_names = length(notnull_c1)+length(notnull_c2)

print(paste("In total",nr_names,"matches on ClinicIDs are found."))
```

```{r Correct ClinicIDs}
nm_ps_raw$country[notnull_c1] <- LUT$country[cid1.idx]
nm_ps_raw$clinic[notnull_c1] <- LUT$c_name[cid1.idx]
nm_ps_raw$clinic_id[notnull_c1] <- LUT$c_id[cid1.idx]
nm_ps_raw$verw_code[notnull_c1] <- "VCID"


nm_ps_raw$country[notnull_c2] <- LUT$country[cid2.idx[notnull_c2]]
nm_ps_raw$clinic[notnull_c2] <- LUT$c_name[cid2.idx[notnull_c2]]
nm_ps_raw$clinic_id[notnull_c2] <- LUT$c_id[cid2.idx[notnull_c2]]
nm_ps_raw$verw_code[notnull_c2] <- "VCID"

sb.idx <- which(nm_ps_raw$verw_code != 'NM')
ps_raw[nm_ps_raw$index[sb.idx], 8:10] <- nm_ps_raw[sb.idx, 8:10]
ps_raw[nm_ps_raw$index[sb.idx], 63] <- nm_ps_raw[sb.idx, 63]

```

Correct country names and check matches

```{r correct CountryNames}
#length(which(ps_raw$verw_code == 'NM'))
# 2279
#length(which(ps_raw$verw_code == 'VCID'))
#[1] 4033
#length(which(ps_raw$verw_code == 'VCIP'))
#[1] 0
#length(which(ps_raw$verw_code == 'VCNM'))
# [1] 16262

# substitute all variances on saudi arabia to 'Saudi Arabia'
ps_raw$country <- sub("^saudi(.*)",'Saudi Arabia', ps_raw$country, ignore.case = TRUE)

# substitute all variances on New Zealand to 'New Zealand'
ps_raw$country <- sub("^New(.*)",'New Zealand', ps_raw$country, ignore.case = TRUE)

# substitute all variances on portugal to 'Portugal'
ps_raw$country <- sub("^portugal(.*)",'Portugal', ps_raw$country, ignore.case = TRUE)

# substitute all variances on portugal to 'Italy'
ps_raw$country <- sub("^italy(.*)",'Italy', ps_raw$country, ignore.case = TRUE)

# substitute all variances on portugal to 'Kazakhstan'
ps_raw$country <- sub("^kazas(.*)",'Kazakhstan', ps_raw$country, ignore.case = TRUE)

ps_raw$verw_code <- as.factor(ps_raw$verw_code)
ps_raw$country <- as.factor(ps_raw$country)
table(ps_raw$country, ps_raw$verw_code)
```
14-11 Update ClinicNames with short names

```{r Change long clinicNames}
update_names <- tbl_df(read.csv2("./data/LUT_v3.csv", sep=',', header=T, colClasses = "character"))

c.idx <- match(ps_raw$clinic_id, update_names$c_id, nomatch=0)
notnull <- which(c.idx != 0)

df <- data.frame(matrix(ncol = 4, nrow = length(notnull)))
df[,1] <- ps_raw$clinic_id[notnull]
df[,2] <- ps_raw$clinic[notnull]
df[,3] <- update_names$c_id[c.idx]
df[,4] <- update_names$c_name[c.idx]

ps_raw$clinic[notnull] <- update_names$c_name[c.idx]

# check whether procedure went ok
#ps_raw$clinic[which(ps_raw$clinic_id == 1502)]
```


Next: Add rowMeans

```{r add RowMeans}
ps_Q <- cbind(ps_raw[,36:41], ps_raw[,43:48], ps_raw[,50:55])
ps_Q <- data.matrix(ps_Q)
rowmeans <- rowMeans(ps_Q, na.rm=T)

ps_raw$rowMeans <- rowmeans
```

Save files

```{r Save Files}
# make header
header <- mat.or.vec(nrow(head), ncol(ps_raw))
header <- cbind(head, header)
header <- rbind(header, names(ps_raw))
header[1,which(header[1,] == 0)] <- ''
header[2,which(header[2,] == 0)] <- ''

ps_raw <- ps_raw[which(ps_raw$verw_code != 'NM'),]
#dim(ps_raw)
#[1] 20295    63

write.table(header[,1:61], file = "data/FINAL/PS/Clean-5783064-11-14-2017.csv", row.names=F, col.names=F,fileEncoding = "UTF-8",sep=',')
write.table(ps_raw[,1:61], file = "data/FINAL/PS/Clean-5783064-11-14-2017.csv", row.names=F, col.names=F,fileEncoding = "UTF-8", append=T, sep=',')

write.table(header[,1:ncol(ps_raw)], file = "data/FINAL/PS/Clean-5783064-11-14-2017-verwerkingcode.csv", row.names=F, col.names=F,fileEncoding = "UTF-8",sep=',')
write.table(ps_raw, file = "data/FINAL/PS/Clean-5783064-11-14-2017-verwerkingcode.csv", row.names=F, col.names=F,fileEncoding = "UTF-8", append=T, sep=',')

print(paste("Saved Qlik file as: data/FINAL/MOC/Clean-5783064-11-14-2017.csv"))
```